---
title: "linear Programming"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown
#### this markdown file is to show a Linear programming problems solved using  Branch and bound method , this approach is used to show that the total feasible solutions can be partitioned into smaller subsete of solutions. these subsets are then evaluated systematically to find the best solution .
```{r}
library(lpSolveAPI)
x <- read.lp("IP_ntomar1.lp")
x
```
```{r}
solve(x)
get.objective(x)
```


```{r}
get.variables(x)
```
####we got the first objective as 41.25 and the values of x1 and x2  are 3.75 and 2.75 respectively , now we need begin the branches by putting a bound on the values of x1 and x2 
#### 1we inroduce the next solution by putting a bound on x1<=3
```{r}
library(lpSolveAPI)
y <- read.lp("IP_ntomar2.lp")
y
```

```{r}
solve(y)
get.objective(y)
get.variables(y)
```
####now the objective function is 30 and values of x1 and x2 is 3 for both . as the solution are integer thus we can stop this branch here .
 
#### 2.we further move to put bound on value of x1 >= 4
```{r}
library(lpSolveAPI)
z <- read.lp("IP_ntomar3.lp")
z
```
```{r}
solve(z)
get.objective(z)
get.variables(z)
```

#### 3.the BOUND of x1 >= 4 and x2 <=1
```{r}
library(lpSolve)
a <- read.lp("IP_ntomar4.lp")
a
```

```{r}
solve(a)
get.variables(a)
get.objective(a)
```
#### 4.the BOUND of x1 <= 4 and x2 <=1 x1 >=4
```{r}
library(lpSolveAPI)
b <- read.lp("IP_ntomar5.lp")
b
```

```{r}
solve(b)
get.objective(b)
get.variables(b)
```
#### 5.bound x1 >= 4;x2 <= 1; x1 >= 5;
```{r}
library(lpSolveAPI)
c <- read.lp("IP_ntomar6.lp")
c
```

```{r}
solve(c)
get.objective(c)
get.variables(c)
```

#### 6.bound x1 >= 4;x2 >= 2;
```{r}
library(lpSolveAPI)
d <- read.lp("IP_ntomar7.lp")
d
```

```{r}
solve(d)
get.variables(d)
get.objective(d)
```

####as the value of x2 here is upto -1e that solution beceomes infeasible , the branch ends here and we move to another branch.

####7. bound x2 <=2 ;
```{r}
library(lpSolveAPI)
e <- read.lp("IP_ntomar8.lp")
e
```

```{r}
solve(e)
get.variables(e)
get.constraints(e)
```
#### 8 . x2 <=2 ;x1 <=3 ;
```{r}
library(lpSolveAPI)
f <- read.lp("IP_ntomar9.lp")
f
```

```{r}
solve(f)
get.objective(f)
get.variables(f)
```
#### 9. x2 <= 2 ;x1 >= 4;
```{r}
library(lpSolveAPI)
g <- read.lp("IP_ntomar10.lp")
g
```

```{r}
solve(g)
get.objective(g)
get.variables(g)
```
####10.bounds  x2 <=2 ;x1 >= 4;x2 <=1;x1 <=4;
```{r}
library(lpSolveAPI)
h <- read.lp("IP_ntomar11.lp")
h
```

```{r}
solve(h)
get.variables(h)
get.constraints(h)
```
#####11.bounds x2 <=2 ;x1 >= 4;x2 <=1;
```{r}
library(lpSolveAPI)
i <- read.lp("IP_ntomar12.lp")
i
```
```{r}
solve(i)
get.variables(i)
get.objective(i)
```

####12.x2 <=2 ;x1 >= 4;x2 <=1;x1 >=5;
```{r}
library(lpSolveAPI)
j <- read.lp("IP_ntomar13.lp")
j
```
```{r}
solve(j)
get.variables(j)
get.objective(j)
```

####13.x2 <=2 ;x1 >= 4;x2 >= 2;
```{r}
library(lpSolveAPI)
k <- read.lp("IP_ntomar14.lp")
k
```

```{r}
solve(k)
get.variables(k)
get.objective(k)
```
###now we put all branch solutions in a csv file and store the result in a variable 'result'

```{r}
result<-read.csv("IP_ntomar.csv")
print(result)
```


####for a better result and comprehension we will take help fo visualisation of our data result and plot 
```{r}
library(ggplot2)
library(esquisse)
library(shiny)
```
```{r}
ggplot(data = result) +
  aes(x = x1, y = x2) +
  geom_line(color = "#0c4c8a") +
  theme_minimal()
```
#### scatter plot of the result

```{r}
ggplot(data = result) +
  aes(x = x1, y = x2) +
  geom_point(color = "#0c4c8a") +
  theme_minimal()
```


